\subsection{Real-World Testing}

\subsubsection{Experimental Methodology}

The system was evaluated through a controlled demonstration comprising both benchtop and short-range field 
testing involving four LoRa nodes, designated Node A through Node D, each operating identical firmware as 
peers within the mesh without any designated coordinator or master node. Nodes were assigned fixed GPS 
coordinates, either physically measured or hardware-mocked, to establish a repeatable spatial geometry 
suitable for isolated testing of each subsystem. Node A served as the message originator across all test 
cases, Nodes B and C functioned as intermediate relay candidates, and Node D served as the terminal receiver. 
Separate monitoring terminals aggregated relay event timestamps and packet logs from all nodes, providing a 
common time reference for cross-node latency measurements. All LoRa transceivers operated at 433~MHz or 
868/915~MHz with a spreading factor of SF9, a bandwidth of 125~kHz, a coding rate of 4/5, and a nominal 
transmit power of +17~dBm, yielding a theoretical sensitivity floor of approximately $-137$~dBm and an 
estimated line-of-sight range of 2~km per hop.

\subsubsection{Multi-Hop Mesh Routing}

To evaluate the multi-hop routing capability, Nodes A and D were separated beyond the single-hop communication 
range achievable under the configured transmit power settings, such that no direct radio path existed between 
them. Node B was positioned at an intermediate point within range of both terminals. A test message was 
transmitted from Node A with a maximum hop count of three. Node B received the packet at an RSSI of 
$-108$~dBm and an SNR of $-3$~dB, delivered the payload to its local application layer, decremented 
the remaining hop count, and relayed the packet following expiration of its computed hold-back delay. 
Node D subsequently received the relayed packet at an RSSI of $-113$~dBm and an SNR of $-5$~dB, confirmed 
local delivery, and terminated the relay chain as no further eligible candidates were within range. End-to-end 
message delivery was completed in under one second of elapsed time, and the hop-count field was confirmed to 
have decremented correctly at each intermediate stage. This result verified that the mesh routing protocol 
successfully extended the effective communication range beyond any individual node's direct transmission 
capability without recourse to pre-configured routing tables or infrastructure elements.

\subsubsection{Priority-Based Delivery}

QoS enforcement was assessed by injecting two messages at Node A in rapid succession, a LOW priority message 
followed by an EMERGENCY priority message at an interval of approximately 1.5~seconds, both routed through 
Node B toward Node C. Node B's relay log recorded a hold-back delay of approximately 320~ms prior to forwarding 
the LOW priority message and approximately 75~ms prior to forwarding the EMERGENCY message. Delivery timestamps 
at Node C confirmed that the EMERGENCY message arrived before the LOW priority message despite having been 
transmitted later. The observed ratio of hold-back delays (approximately $4.3\times$) was consistent with the 
intended fourfold priority scaling encoded in the delay computation formula, confirming that the QoS 
classification mechanism correctly propagated priority distinctions across at least one relay hop and 
remained effective when messages from different priority tiers were simultaneously queued at an intermediate node.

\subsubsection{Directional Propagation}

The geographic propagation control mechanism was evaluated using a five-node configuration in which Nodes 
B, C, and D were positioned within a northward angular arc of approximately $\pm 40^\circ$ relative to Node 
A, while Node E was placed at a bearing of approximately $120^\circ$ east of north, well outside any $\pm 45^\circ$ 
directional cone aligned northward. In OMNI mode, a broadcast message with a maximum hop count of two was 
received and relayed by all four surrounding nodes, producing five total relay events including the 
origination transmission. The test was repeated in DIRECTIONAL mode with a target heading of $0^\circ$ (due north), 
defining a $\pm 45^\circ$ propagation cone. Nodes B, C, and D, all falling within the cone, received and relayed 
the message as expected. Node E received the packet and delivered it locally, confirming successful radio 
reception, but its network layer computed the bearing from Node A to Node E as $120^\circ$ from north, 
determined this to exceed the cone boundary, and suppressed re-transmission in accordance with the deliver-only 
policy. The transition from OMNI to DIRECTIONAL mode reduced the total number of relay events by 40\% for this 
topology, and the geographic filtering operated entirely autonomously at each node through independent 
Haversine-based bearing computation against coordinates embedded in the packet header, requiring no centralized 
arbitration.

\subsubsection{Intelligent Relay Timing}

The hold-back mechanism was evaluated by placing three relay candidates, Nodes B, C, and D, at distances 
of approximately 200~m, 900~m, and 1.6~km from Node A, respectively. The corresponding received signal 
conditions were: Node B at $-85$~dBm RSSI and $+6$~dB SNR, Node C at $-105$~dBm RSSI and $-1$~dB SNR, and 
Node D at $-118$~dBm RSSI and $-7$~dB SNR. A single MEDIUM priority message was broadcast from Node A, and 
all three candidates received the packet simultaneously. Each node independently computed its hold-back delay 
from its locally measured signal quality. Node D, the most distant node with the weakest received signal, 
relayed first at approximately 82~ms after the originating transmission. Node C relayed at approximately 
194~ms. Node B, the closest node with the strongest received signal, computed a hold-back delay of approximately 
340~ms; however, before this timer expired, it detected Node C's re-transmission of the same packet, 
identified by matching the originator identifier and sequence number, and cancelled its own pending relay. 
The result was two actual relay transmissions from three candidate nodes, representing a 33\% reduction in 
redundant channel occupancy for this configuration. The observed relay ordering, farthest node first and closest 
node suppressed, constitutes the intended emergent behavior of the signal-quality-weighted delay formula and 
confirms that distributed best-relay selection was achieved without any explicit inter-node negotiation.

\subsubsection{Summary}

Across all four evaluated subsystems, the system performed in accordance with its design specifications. 
No routing loops, duplicate final deliveries, or spurious relay activations were observed during the 
evaluation period. The collective results substantiate the proposition that a fully distributed, 
infrastructure-free vehicular mesh network can enforce message priority, geographic propagation boundaries, 
and efficient relay selection using only information embedded within each packet and signal quality 
parameters measurable locally at each receiving node.