\subsection{Simulation}

The simulation study was designed as a deterministic host-side validation environment for the network-layer 
logic, with the primary objective of evaluating forwarding behavior under controlled channel and mobility 
conditions without dependence on embedded timing artifacts. Rather than introducing an alternative protocol 
formulation, the study preserved the same network-layer decision process used in deployment and exercised it 
through a virtualized communication context. This design choice ensured that observed behavior reflected 
routing and suppression policy interactions, not differences between production and test code paths.

The scope of evaluation covered both transport-level effects and network-layer forwarding semantics. The 
simulation environment modeled virtual time progression, topology evolution, and configurable channel 
impairments, while the forwarding pipeline remained unchanged at each node. Consequently, outcome traces 
could be interpreted as direct evidence of how duplicate handling, relay delay policy, and hop-limited 
dissemination behaved under reproducible operating scenarios. The methodology followed a staged progression 
from baseline delivery correctness to forwarding-policy validation and then to determinism and scalability stress.

Time evolution was governed by an explicit virtual clock to eliminate host scheduling jitter from causal 
ordering. Scenario progression occurred only through deliberate time advancement, allowing tests to assert 
not only eventual delivery but also the absence of premature delivery under insufficient elapsed time. 
Event processing followed a stable ordering policy, so concurrent transmissions, deferred relays, and 
queued channel actions were resolved consistently across repeated runs. This deterministic execution model 
was essential for separating protocol behavior from platform variability and for supporting strict regression 
comparison.

Scenario specification exposed controlled configuration of channel timing, impairment intensity, congestion 
behavior, and randomization seed, together with per-node initial state and mobility evolution. Mobility was 
represented as deterministic kinematic progression with scheduled state updates, enabling reproducible 
transitions between disconnected and connected topologies. Because topology change and event processing 
were integrated into a single ordered step sequence, the exact virtual time at which connectivity shifted 
could be asserted and reproduced.

The channel model combined distance-dependent attenuation with receiver sensitivity gating and optional 
stochastic impairment mechanisms. Under this model, reception depended on whether signal conditions remained 
admissible at the receiver, while optional packet-error and congestion-driven loss mechanisms introduced 
controlled non-ideal behavior. For stochastic branches, pseudo-random decisions were seed-controlled and 
tied to event identity, so fixed seeds yielded identical outcomes and different seeds yielded intentional 
divergence. This balance enabled both deterministic verification and sensitivity studies without changing 
core forwarding logic.

Validation was performed through a reusable harness that captured application-visible deliveries at each 
node and compared both payload content and dissemination structure. Assertions were made using stepped 
virtual-time progression, permitting precise checks on temporal causality, deferred forwarding, and 
timeout-related behavior. In parallel, aggregate channel and delivery metrics were collected to quantify 
retransmission activity, collision effects, packet-error losses, congestion drops, latency trends, and 
utilization levels. The combined use of trace-level and aggregate evidence strengthened confidence in 
both functional correctness and system-level behavior.

Baseline results confirmed expected fan-out properties for broadcast dissemination, preservation 
of payload integrity, and correct exclusion of sender self-delivery. Reachability outcomes tracked 
configured radio conditions: nearby receivers were served under admissible signal budgets, while 
distant receivers were excluded until mobility brought them into effective communication range. 
These observations established that delivery behavior remained consistent with geometric and sensitivity 
constraints before higher-order forwarding policies were considered.

Temporal and channel-access evaluations demonstrated that delivery in timed operation depended 
on sufficient virtual-time advancement and that channel contention produced deferred transmissions 
rather than uncontrolled immediate rebroadcast. Under concurrent access, overlapping activity produced 
measurable collision-related failures, while controlled deferral and retry behavior maintained bounded 
progression. Propagation-delay experiments further showed physically consistent ordering in which nearer 
receivers could observe arrival before farther receivers under equal transmission origin.

Impairment and load experiments verified that packet-error and congestion mechanisms affected delivery 
in expected directions. Strict error thresholds and forced congestion regimes reduced successful receptions 
and increased drop-related counters, whereas light-load regimes below congestion thresholds preserved 
delivery continuity. These outcomes indicate that the simulation could represent both nominal and 
stressed channel conditions while retaining deterministic interpretability.

Most importantly, forwarding-semantics validation under simulation confirmed correct behavior for 
lifetime-bounded dissemination, directional relay eligibility, multi-hop reach extension, and 
duplicate suppression at application-delivery boundaries. Lifetime constraints prevented stale 
forwarding beyond configured validity windows, directional policy constrained relay participation 
according to propagation intent, and relaying extended delivery to nodes outside direct source reach. 
When redundant copies arrived through distinct paths, delivery remained idempotent at the receiver 
interface, demonstrating effective suppression of duplicate application exposure.

Scalability and repeatability assessments provided additional evidence of practical robustness. 
Large-node broadcast workloads sustained expected dissemination coverage, and higher-node stepping 
workloads remained within practical runtime budgets for host-based evaluation. Repeated executions 
with identical seeds produced stable dissemination snapshots, while seed variation produced controlled 
stochastic differences. Together, these findings support the claim that the framework offers deterministic 
regression capability and controlled variability analysis within a single unified methodology.

The results should be interpreted within the model assumptions. Propagation behavior was represented 
through analytic attenuation with configurable impairment terms rather than a fully site-calibrated 
empirical urban channel model, and contention behavior was abstracted at event level rather than 
modeled through complete physical-layer waveform interaction. Accordingly, the study provided strong 
evidence of network-layer logical correctness, timing consistency, and resilience under modeled 
conditions, while not claiming full physical-fidelity prediction for all deployment environments.

Overall, the simulation campaign supplied coherent evidence of logical correctness, timing consistency, 
and forwarding behavior under modeled nominal and adverse conditions. By combining deterministic virtual-time 
execution, policy-focused scenario design, and complementary trace and metric assertions, this section 
establishes a reproducible baseline that is complemented by the real-world measurements reported in the 
next subsection.