\section{Problem Statement}

\subsection{Problem Definition}

This project addresses the design and validation of an infrastructure-free Vehicle-to-Vehicle
(V2V) communication system for cooperative safety-message dissemination. The work is motivated by a practical
project constraint: LoRa hardware was available and affordable for implementation, making it suitable for
building and evaluating a complete prototype in our academic setting. The target is therefore not to compete
with purpose-built DSRC/C-V2X deployment ecosystems, but to answer a narrower technical question: can a
\textit{fully decentralized} vehicular mesh achieve reliable and efficient multi-hop safety dissemination
using only local observations and peer-to-peer forwarding.

The problem is challenging because LoRa links impose strict communication constraints, including low data rate,
long Time-on-Air, duty-cycle limits, and shared-medium contention \cite{lora_mesh_iot,routing_mesh_2020}.
Without careful protocol control, these constraints can lead to excessive collisions, redundant rebroadcast,
and unstable dissemination behavior in dynamic vehicular topologies \cite{vdtn_routing_eval,lora_mesh_emergency}.
Hence, the central problem is to design a decentralized protocol stack that preserves dissemination reach while
keeping channel usage bounded and operational behavior predictable.

\subsection{Objectives and Goals}

The project objectives are:

\begin{itemize}
	\item Design a three-layer architecture with clear separation between application logic, forwarding control,
	and radio-facing transmission services.
	\item Implement decentralized network-layer dissemination using managed flooding, duplicate suppression,
	hop-bounded propagation, and policy-aware relay timing.
	\item Implement link-layer channel-aware behavior, including sensing-driven transmission admission and
	optional reliability signaling for critical traffic classes.
	\item Validate the same logical forwarding behavior in both deterministic simulation and real-node testing,
	so results can be compared across controlled and field-like conditions.
	\item Demonstrate that the system can deliver safety messages across multiple hops with bounded redundancy,
	without dependence on RSUs, fixed gateways, or centralized coordination.
\end{itemize}

\subsection{Significance of the Problem}

Solving this problem is significant at three levels. First, it provides a low-cost and reproducible platform
for studying decentralized vehicular networking in a college project environment. Second, it contributes
practical evidence on infrastructure-free dissemination behavior for scenarios where fixed communication
support may be sparse or temporarily unavailable \cite{lora_mesh_emergency,lora_reliable_v2v_2025}. Third,
it demonstrates an engineering pathway in which identical network-layer logic can be exercised in simulation
and embedded deployment, improving confidence in protocol behavior before wider real-world scaling.

