\subsection{Link Layer Architecture}

The link-layer architecture operationalized the communication semantics required by the upper stack while 
preserving strict boundaries with routing and application logic. Its principal responsibility was to provide 
a dependable single-hop delivery substrate over a constrained long-range channel, including frame construction, 
channel access coordination, reception management, and controlled energy behavior. In this design, upper layers 
submitted payloads and consumed delivery events through an asynchronous service interface, whereas all 
radio-facing behavior remained encapsulated within the link layer. This separation ensured that forwarding 
policy, topology reasoning, and service semantics could evolve independently of modem-specific constraints.

The wire format was organized around a compact fixed-size header followed by a bounded payload region, 
thereby ensuring deterministic parsing cost and explicit interoperability guarantees across nodes. Header 
fields encoded source and destination identifiers, message classification, sequence numbering, control flags, 
and payload length. The addressing model used node-local unicast identifiers and a dedicated broadcast 
destination value for one-to-many dissemination. Sequence and flag metadata jointly supported reliability 
signaling without imposing mandatory overhead on all traffic classes. A reserved message type was allocated 
for acknowledgment control traffic, preventing ambiguity between reliability signaling and application-defined 
data categories.

Medium access control followed a listen-before-send strategy based on channel activity detection. Prior to 
transmission, the transmitter assessed channel occupancy and deferred when LoRa activity was detected, 
reducing collision probability under shared medium contention. When repeated busy indications occurred, 
bounded retry behavior with randomized backoff was applied to decorrelate concurrent transmitters and limit 
persistent synchronization effects. If the medium remained unavailable beyond the configured sensing budget, 
the pending transmission was discarded to prevent unbounded latency growth and queue destabilization. 
This policy favored predictable temporal behavior and spectrum discipline over aggressive persistence.

The transmission workflow combined queued frame dispatch with optional per-frame reliability. Once admitted 
for transmission, a frame underwent channel sensing and, when clear, was emitted over the radio interface. 
For traffic that did not request reliability, completion ended at transmit confirmation. For reliability-enabled 
traffic, the sender entered a bounded acknowledgment wait phase and validated incoming acknowledgments against 
sequence and addressing context. Successful matches terminated the transaction with positive outcome signaling 
to the upper layer. Timeout events triggered controlled retransmission attempts up to a configured maximum, 
after which the frame was reported as undelivered. This selective reliability model allowed critical safety 
messages to request stronger delivery assurance while preserving lower overhead for noncritical traffic.

Inbound processing followed a strict filtering pipeline to protect upper-layer logic from malformed or 
irrelevant traffic. Frames below the minimum valid length were rejected immediately. Valid frames were parsed, 
and link-quality observations were recorded for neighbor awareness. Destination filtering then removed packets 
not addressed to the local node or broadcast group. Pure acknowledgment frames were consumed internally by the 
reliability subsystem and not exposed as application payload events. When a received data frame requested 
acknowledgment, a corresponding acknowledgment response was generated at link level. Only after these checks 
were satisfied was payload data delivered upward, ensuring that upper layers observed semantically meaningful 
and policy-compliant traffic.

Energy management was integrated into runtime behavior through adaptive receive-idle control. 
The receiver remained active to preserve responsiveness but transitioned to a low-power modem state 
after sustained inactivity. Wake-up was event-driven: outbound traffic demand or relevant radio interrupt 
activity restored active operation and resumed normal processing. This approach balanced readiness and battery 
efficiency, a necessary trade-off for vehicular platforms that must sustain long operating intervals without 
sacrificing timely communication when events occur.

Hardware abstraction was achieved through a backend interface that isolated protocol and state logic from 
concrete transceiver drivers. The link layer relied on this contract for channel sensing, transmission, 
reception, signal-quality observation, interrupt signaling, and power-state transitions. As a consequence, 
the same link-layer behavior could execute against production radio hardware or controlled test backends 
without architectural change. This design improved portability, enabled deterministic validation under 
laboratory conditions, and reduced coupling between communication policy and platform-specific implementation 
details.

