\subsection{Network Layer Architecture}

The network layer constituted the control plane of the proposed LoRa-based vehicle-to-vehicle system and 
was designed as a portable, hardware-independent core positioned between application services and radio-facing 
transmission services. Its architectural role was to transform locally generated safety data into 
dissemination-ready network frames, to evaluate received frames against propagation policy, and to 
regulate rebroadcast behavior so that dissemination reliability could be improved without incurring unnecessary 
channel occupation. This role was realized through explicit boundary abstractions that isolated forwarding 
intelligence from platform-specific communication and sensing mechanisms, thereby allowing identical network 
behavior to be preserved across embedded deployments and host-side simulation environments.

At the transmission boundary, each outgoing frame was structured as a fixed network header followed by 
application payload bytes. The header encoded message identity, temporal validity, origin context, per-hop 
transmitter context, and propagation constraints, so that downstream nodes could make forwarding decisions 
from self-contained frame metadata. The fixed header length established deterministic parsing and bounded 
overhead, while the payload limit was derived directly from the LoRa frame-size ceiling to guarantee that 
all generated frames remained admissible for the underlying physical channel. Within this model, a unique 
message identifier combined source identity with a local sequence progression, enabling replay suppression 
and idempotent handling throughout multi-hop dissemination.

The layer distinguished immutable origin metadata from mutable per-hop transmitter metadata as a central 
design principle. Origin metadata remained unchanged for the lifetime of a message and represented the initial 
source state at creation time. By contrast, transmitter metadata was refreshed at every relay and represented 
the most recent forwarding node. This semantic separation enabled the routing process to reason simultaneously 
about global propagation intent and local progression, which was essential for both hold-back scheduling and 
redundancy suppression in dynamic vehicular topologies.

Operationally, the data plane followed two coordinated paths: synchronous origination and asynchronous 
reception-driven forwarding. During origination, the layer validated payload admissibility, assembled the 
network header using local temporal and mobility context, registered the message identity in a duplicate-tracking 
structure, and emitted a single broadcast frame. During reception, incoming frames were first buffered through 
a bounded event queue and then processed by worker execution contexts that performed parse, policy evaluation, 
local delivery, and conditional relay scheduling. This decoupled architecture prevented receive callbacks from 
becoming policy execution bottlenecks and improved temporal predictability under bursty traffic.

Forwarding decisions were produced by an ordered evaluation pipeline that prioritized safety and bounded 
propagation. Frames were first screened for temporal expiry, replay status, and residual hop budget, 
followed by checks on distance-constrained dissemination and directional eligibility when directional 
propagation was requested. Messages that satisfied these gates were considered relay candidates and assigned 
a deferred forwarding delay rather than immediate retransmission. The delay was computed from a composite 
estimate of path progress and link quality, and then modulated by traffic priority so that urgent safety 
traffic propagated with lower latency while less critical traffic was naturally delayed. This mechanism 
implemented contention-aware spatial diversity by encouraging favorable relays to transmit earlier and 
discouraging simultaneous redundant rebroadcasts.

To further limit broadcast redundancy, the architecture incorporated two complementary suppression mechanisms. 
First, duplicate filtering prevented repeated processing and forwarding of already observed message identities. 
Second, queued relays could be canceled when subsequently overheard transmissions indicated that upstream 
progression had already covered the local node's prospective forwarding contribution. This geometric suppression 
strategy reduced superfluous retransmissions without requiring explicit coordination exchanges, which is 
advantageous in bandwidth-constrained and intermittently connected vehicular channels.

Concurrency management was integral to architectural correctness. The network layer employed separate execution 
contexts for receive-path processing and timer-driven relay emission, with mutex- and condition-variable-based 
synchronization around bounded shared queues and callback handoff state. Lifecycle control was designed to be 
robust under repeated start-stop operation, ensuring deterministic initialization, safe termination of background 
activity, and clean release of receive handlers during shutdown. This threading model provided clear separation 
between ingress handling, routing computation, and deferred transmission timing.

The architecture also exposed bounded configuration controls that governed duplicate-cache capacity, relay-queue 
capacity, receive-queue depth, and forwarding delay limits. These parameters defined the operational envelope 
for memory consumption, latency, and admission behavior, and therefore enabled systematic trade-off analysis 
between responsiveness and channel load. In combination with fixed frame-level constraints, the configuration 
model promoted predictable runtime behavior across heterogeneous hardware targets.

Finally, the same network-layer core was embedded in a deterministic simulation runtime to support repeatable 
validation under controlled mobility and channel conditions. Each simulated node instantiated the same logical 
network functionality as a deployed node, while a shared virtual clock and event-driven channel model governed 
transmission timing, reception outcomes, and channel impairments. Because routing and forwarding semantics were 
preserved across deployment and simulation, the architecture supported direct transfer of behavioral findings 
from laboratory evaluation to field-oriented configurations.

